---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mladv

mladv is a r package used to clean, convert and analyze the financial data. It also provides various tools to apply machine learning to financial data.

## Installation

You can install the released version of mladv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("mladv")
```

We expect to release the package as soon as possible in CRAN. At the mean time, you can install it with devtools: 

```r
devtools::install_github("thanhuwe8/mladv")
```

## Example

First you load the data from the package

```{r example}
library(mladv)
data(SSI_data)
head(SSI_data,3)
```

With the data_set, we can convert the raw market data into different bars such as time bars or volume bars as examples below with `SSI_data`

```{r volumebarr}
volume6000 <- volumebarr(SSI_data, 15000)
head(volume6000)
```

```{r timebar}
minute_bar <- timebar(SSI_data, "minute")
head(minute_bar)
```

We can still use functions from popular packages such as `quantmod` or `ggplot2` with the return data.frame 

```{r quantmodplot}
library(xts)
library(quantmod)
minute_plot <- xts(minute_bar[,2:6], order.by=minute_bar$Date)
candleChart(minute_plot, theme="white", multi.col=T, name="Minute bar chart")
```


We will add more useful functions later.
