---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mladv

The package `mladv` provide tools to clean, convert and analyze the financial data. It also provides various tools to apply machine learning to financial data.

## Installation

We expect to release the package as soon as possible in [CRAN](https://CRAN.R-project.org). At the mean time, you can install it with devtools: 

```r
devtools::install_github("thanhuwe8/mladv")
```

## Example

First you load the data from the package

```{r example}
library(mladv)
head(data1,3)
```

With the data_set, we can convert the raw market data into different bars such as time bars or volume bars as examples below with `SSI_data`

```{r volumebarr}
volume6000 <- volumebarr(data1, 15000)
head(volume6000)
```

```{r timebar}
minute_bar <- timebar(data1, "minute")
head(minute_bar)
```

We can still use functions from popular packages such as `quantmod` or `ggplot2` with the return data.frame 


We will add more useful functions later.

# License
This project is licensed under the GPL3 License
